\Large \bf \projtitle

### 2015-05-08 doc/paper/paper.tex
added missing citations
Add testing infrastructure section

% TODO selenium with chromedriver & scala
% anish should probably do this section

@@

\subsection{Support for HTML5 media}
It is possible to add functionality such that \zbf can construct
\texttt{ReadableStream}s (as specified by the Streams standard)
%TODO: cite https://streams.spec.whatwg.org
from the chunks of data as it receives them. Using this stream, the DOM injection
layer could feasibly replace HTML5 media elements such as embedded Video and Audio.
Since these types of media are particularly large in size, being able to distribute
them in a decentralized, peer-to-peer manner could provide substantial load
reduction for the central server.

@@

%! TODO cite peercdn in bibtex
Currently, alternative peer-to-peer content delivery networks do exist. The three
prominent peer-to-peer CDNs are PeerJS, PeerCDN, and Peer5. PeerJS is open-sourced
and similarly transparent, but only encapsulates the functionality of our connection manager
module. PeerCDN~\cite{peercdn} is a closed-source alternative providing  similar
functionality to \zbf; it offloads site content delivery to users of a site,
significantly lowering strain on the central source. However, PeerCDN was acquired by
Yahoo! and no longer exists. Finally, Peer5 is a service used by companies today.
Unfortunately, Peer5 is a paid service that is entirely closed-source; the Peer5 code is
not transparent to the clients on which it runs.

>>>>

Our testing infrastructure was made up of a virtual machine hosting our
website, a tracker running on the host machine, and a collection of web
browsers acting as clients. All test code ran on the same physical machine. We
used Vagrant to provision an Ubuntu 14.04 LTS virtual machine running nginx
1.4.6 to serve a test page designed for benchmarking. To simulate a
low-resource server / heavy loads, we used kernel traffic shaping to limit the
outbound bandwidth of the virtual machine. To simulate browser clients, we
wrote a test driver in Scala that made use of Selenium WebDriver and
ChromeDriver to launch and control Google Chrome browser windows. The test
driver spawned and communicated with browser windows and benchmark code through
Javascript so it could measure page load times.

@@

\subsection{Support for HTML5 media}
It is possible to add functionality such that \zbf can construct
\texttt{ReadableStream}s (as specified by the Streams standard~\cite{whatwg:streams})
from the chunks of data as it receives them. Using this stream, the DOM injection
layer could feasibly replace HTML5 media elements such as embedded Video and Audio.
Since these types of media are particularly large in size, being able to distribute
them in a decentralized, peer-to-peer manner could provide substantial load
reduction for the central server.

@@

Currently, alternative peer-to-peer content delivery networks do exist. The three
prominent peer-to-peer CDNs are PeerJS, PeerCDN, and Peer5. PeerJS is open-sourced
and similarly transparent, but only encapsulates the functionality of our connection manager
module. PeerCDN~\cite{peercdn} is a closed-source alternative providing  similar
functionality to \zbf; it offloads site content delivery to users of a site,
significantly lowering strain on the central source. However, PeerCDN was acquired by
Yahoo! and no longer exists. Finally, Peer5 is a service used by companies today.
Unfortunately, Peer5 is a paid service that is entirely closed-source; the Peer5 code is
not transparent to the clients on which it runs.
